---
title: "HindiBabyNet Vocal Input and Child Output Model Report"
author: "Arun Prakash Singh"
date: "`r format(Sys.Date(), '%d %B %Y')`"
output:
  pdf_document:
    toc: yes
  html_document:
    theme: flatly
    toc: yes
    toc_float: yes
    number_sections: yes
    code_folding: show
    df_print: paged
params:
  refit_models: yes
  nsim: 100
  model_robustness_mode: "strict" #"strict" or "auto"
  family1_count_age_specification: "quadratic" # "none", "linear", or "quadratic"
  family1_duration_age_specification: "quadratic" # "none", "linear", or "quadratic"
  family2_count_age_specification: "quadratic" # "none", "linear", or "quadratic"
  family2_duration_age_specification: "quadratic" # "none", "linear", or "quadratic"
  anova_type: 2 # 2 or 3
  response_transform_global: "none"
  response_transform_map: ""
  family1_participant_intercept: "with" # "with" or "without"
  family1_location_intercept: "without"
  family1_drop_fixed_terms:  ["speaker:age_z2"] #!r character(0) # ["fixed_effect1", fixed_effect2] #["speaker:age_z", "speaker:age_z2"] #
  family1_extra_fixed_terms: !r character(0)
  family1_random_slope_terms: !r character(0)
  family2_participant_intercept: "without"
  family2_location_intercept: "without"
  family2_drop_fixed_terms: !r character(0) # ["input_count_hour:speaker", "input_duration_min_hour:speaker"]#
  family2_extra_fixed_terms: !r character(0)
  family2_random_slope_terms: !r character(0) # ["speaker|participant_id"]
  show_code: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = params$show_code,
  warning = FALSE,
  message = FALSE,
  fig.align = "center",
  fig.width = 9,
  fig.height = 5.5,
  dpi = 120
)

options(width = 120, scipen = 999)

collapse_param_values <- function(values) {
  if (is.null(values) || length(values) == 0) {
    return("")
  }

  values <- trimws(as.character(unlist(values, use.names = FALSE)))
  values <- values[nzchar(values)]
  if (length(values) == 0) {
    return("")
  }

  paste(values, collapse = ";")
}

apply_report_environment_overrides <- function() {
  age_specification_map <- paste(
    c(
      sprintf("family1_count=%s", params$family1_count_age_specification),
      sprintf("family1_duration=%s", params$family1_duration_age_specification),
      sprintf("family2_count=%s", params$family2_count_age_specification),
      sprintf("family2_duration=%s", params$family2_duration_age_specification)
    ),
    collapse = ","
  )

  Sys.setenv(
    HBN_NSIM = as.character(params$nsim),
    HBN_MODEL_ROBUSTNESS_MODE = as.character(params$model_robustness_mode),
    HBN_AGE_SPECIFICATION = "",
    HBN_AGE_SPECIFICATION_MAP = age_specification_map,
    HBN_ANOVA_TYPE = as.character(params$anova_type),
    HBN_RESPONSE_TRANSFORM_GLOBAL = as.character(params$response_transform_global),
    HBN_RESPONSE_TRANSFORM_MAP = as.character(params$response_transform_map),
    HBN_FAMILY1_PARTICIPANT_INTERCEPT = as.character(params$family1_participant_intercept),
    HBN_FAMILY1_LOCATION_INTERCEPT = as.character(params$family1_location_intercept),
    HBN_FAMILY1_DROP_FIXED_TERMS = collapse_param_values(params$family1_drop_fixed_terms),
    HBN_FAMILY1_EXTRA_FIXED_TERMS = collapse_param_values(params$family1_extra_fixed_terms),
    HBN_FAMILY1_RANDOM_SLOPES = collapse_param_values(params$family1_random_slope_terms),
    HBN_FAMILY2_PARTICIPANT_INTERCEPT = as.character(params$family2_participant_intercept),
    HBN_FAMILY2_LOCATION_INTERCEPT = as.character(params$family2_location_intercept),
    HBN_FAMILY2_DROP_FIXED_TERMS = collapse_param_values(params$family2_drop_fixed_terms),
    HBN_FAMILY2_EXTRA_FIXED_TERMS = collapse_param_values(params$family2_extra_fixed_terms),
    HBN_FAMILY2_RANDOM_SLOPES = collapse_param_values(params$family2_random_slope_terms)
  )
}

apply_report_environment_overrides()

source(file.path("R", "00_setup.R"))
source(file.path("R", "functions", "data_prep.R"))
source(file.path("R", "functions", "model_selection.R"))
source(file.path("R", "functions", "model_diagnostics.R"))
source(file.path("R", "functions", "monte_carlo_ci.R"))
source(file.path("R", "functions", "prediction_plots.R"))
source(file.path("R", "functions", "reporting.R"))

load_required_packages(attach = FALSE)
ensure_analysis_directories()

apply_report_analysis_overrides <- function() {
  analysis_options$nsim_default <- params$nsim
  analysis_options$model_robustness_mode <- params$model_robustness_mode
  analysis_options$family_2_participant_intercept <- params$family2_participant_intercept
  analysis_options$model_spec_overrides <- list(
    family_1 = list(
      participant_intercept = params$family1_participant_intercept,
      location_intercept = params$family1_location_intercept,
      drop_fixed_terms = as.character(unlist(params$family1_drop_fixed_terms, use.names = FALSE)),
      extra_fixed_terms = as.character(unlist(params$family1_extra_fixed_terms, use.names = FALSE)),
      random_slopes = as.character(unlist(params$family1_random_slope_terms, use.names = FALSE))
    ),
    family_2 = list(
      participant_intercept = params$family2_participant_intercept,
      location_intercept = params$family2_location_intercept,
      drop_fixed_terms = as.character(unlist(params$family2_drop_fixed_terms, use.names = FALSE)),
      extra_fixed_terms = as.character(unlist(params$family2_extra_fixed_terms, use.names = FALSE)),
      random_slopes = as.character(unlist(params$family2_random_slope_terms, use.names = FALSE))
    )
  )
}

apply_dataset_runtime_state <- function(datasets_bundle) {
  analysis_options$age_days_mean <- datasets_bundle$age_days_mean
  analysis_options$age_days_sd <- datasets_bundle$age_days_sd
  analysis_runtime$age_days_mean <- datasets_bundle$age_days_mean
  analysis_runtime$age_days_sd <- datasets_bundle$age_days_sd
}

apply_report_analysis_overrides()

# Packages used only for rendering readable report tables.
if (!requireNamespace("knitr", quietly = TRUE)) {
  stop("Package 'knitr' is required to render this report.")
}

show_table <- function(x, digits = 3, caption = NULL) {
  if (is.null(x) || nrow(as.data.frame(x)) == 0) return(invisible(NULL))
  print(knitr::kable(as.data.frame(x), digits = digits, caption = caption))
  invisible(x)
}

bind_rows_safe <- function(items) {
  non_empty <- Filter(Negate(is.null), items)
  if (length(non_empty) == 0) {
    return(data.frame())
  }

  all_columns <- unique(unlist(lapply(non_empty, names), use.names = FALSE))
  aligned <- lapply(non_empty, function(item) {
    missing_columns <- setdiff(all_columns, names(item))
    for (column in missing_columns) {
      item[[column]] <- NA
    }
    item[all_columns]
  })

  do.call(rbind, aligned)
}

fixed_effects_table <- function(bundle) {
  tidy_model_fixed_effects(bundle$model, conf.int = TRUE)
}

random_effects_table <- function(bundle) {
  tryCatch(
    tidy_model_random_effects(bundle$model, conf.int = TRUE),
    error = function(e) data.frame(note = conditionMessage(e))
  )
}

model_fit_table <- function(bundle) {
  data.frame(
    response = bundle$response_name,
    model_family = bundle$model_family,
    selected_model = bundle$selection$model_type[[1]],
    age_specification = bundle$age_specification %||% analysis_options$model_config$age_specification,
    response_transform = bundle$response_transform %||% "none",
    n_complete_cases = bundle$n_complete_cases,
    AIC = AIC(bundle$model),
    BIC = BIC(bundle$model),
    logLik = as.numeric(logLik(bundle$model)),
    formula = paste(deparse(bundle$fitted_formula), collapse = " "),
    stringsAsFactors = FALSE
  )
}

anova_display_table <- function(bundle) {
  anova_result <- tryCatch(
    car::Anova(bundle$model, type = analysis_options$model_config$anova_type),
    error = function(e) e
  )

  if (inherits(anova_result, "error")) {
    return(data.frame(note = conditionMessage(anova_result), stringsAsFactors = FALSE))
  }

  anova_frame <- as.data.frame(anova_result, stringsAsFactors = FALSE)
  anova_frame$term <- rownames(anova_frame)
  rownames(anova_frame) <- NULL
  anova_frame[, c("term", setdiff(names(anova_frame), "term")), drop = FALSE]
}

vif_display_table <- function(bundle) {
  as.data.frame(vif_table(bundle), stringsAsFactors = FALSE)
}

write_report_table <- function(table, filename) {
  utils::write.csv(as.data.frame(table), file.path(analysis_paths$results_tables, filename), row.names = FALSE)
  invisible(table)
}

read_optional_csv <- function(path) {
  if (!file.exists(path)) {
    return(NULL)
  }
  utils::read.csv(path, stringsAsFactors = FALSE, check.names = FALSE)
}

print_model_summary <- function(bundle) {
  cat("\n### Full model summary\n\n")
  print(summary(bundle$model))
}

show_saved_image <- function(path, caption = NULL) {
  if (!is.null(path) && length(path) == 1 && !is.na(path) && file.exists(path)) {
    print(knitr::include_graphics(path))
  } else {
    cat("Plot was not produced.\n")
  }
}
```

# 1. Purpose and execution order

This report runs the complete R modelling workflow in the following order:

1.  load and validate the public analysis datasets;
2.  inspect each response and select its model type;
3.  fit or load the four preregistered model bundles;
4.  display model-selection decisions and model summaries;
5.  display fixed and random effects tables;
6.  generate prediction intervals and publication figures;
7.  run and display model diagnostics;
8.  save the same model, table, prediction, plot, and diagnostic files used by the scripted workflow.

Set `params$refit_models` to `false` when the `.rds` model bundles already exist and you only want to rebuild the report. `params$nsim` controls the number of parametric bootstrap simulations for LMM prediction intervals. A larger value gives more stable intervals but takes longer.

Use the parameter block at the top of this file to control fixed effects, random intercepts, and random slopes for both Family 1 and Family 2. `params$model_robustness_mode` accepts `"auto"` or `"strict"`. In `"auto"` mode, the workflow tries your requested specification first and then simplifies it if needed so the report still completes. In `"strict"` mode, it uses only the exact requested specification and stops if that model cannot be fit.

In the statistical models, SES is treated as an ordered numeric predictor named `SES_num`, derived from the original `SES` labels using this fixed mapping: `primary_school = 1`, `high_school = 2`, `Intermediate = 3`, `bachelor = 4`, and `master = 5`.

Age is configured centrally through four per-model settings: `params$family1_count_age_specification`, `params$family1_duration_age_specification`, `params$family2_count_age_specification`, and `params$family2_duration_age_specification`. `"none"` removes age from the fixed-effects structure, `"linear"` uses `age_z`, and `"quadratic"` uses both `age_z` and `age_z2`, where the z-scores are computed directly from age in days. Response-scale transforms are configured through either `params$response_transform_global` or `params$response_transform_map`. When `response_transform_global` is non-empty, it takes precedence and the per-response map is ignored.

# 1.1 What to change in this .Rmd file

Edit the `params:` block at the top of this file.

- `family1_participant_intercept` and `family2_participant_intercept`: set to `"with"`, `"without"`, or `"auto"`.
- `family1_location_intercept` and `family2_location_intercept`: set to `"with"`, `"without"`, or `"auto"`.
- `family1_drop_fixed_terms` and `family2_drop_fixed_terms`: list the fixed-effect terms you want removed. Use `SES_num` if you want to remove the continuous SES term.
- `family1_extra_fixed_terms` and `family2_extra_fixed_terms`: list extra fixed-effect terms you want added.
- `family1_random_slope_terms` and `family2_random_slope_terms`: list random slope terms using `term|group`, `term||group`, or full lme4 syntax such as `(1 + speaker | participant_id)`.
- `model_robustness_mode`: use `"auto"` for safe experimentation or `"strict"` for exact-spec fitting only.
- `family1_count_age_specification`, `family1_duration_age_specification`, `family2_count_age_specification`, and `family2_duration_age_specification`: use `"none"`, `"linear"`, or `"quadratic"` to control the age terms for each model separately.
- `response_transform_global`: set one transform for all responses using `"none"`, `"log"`, or `"log1p"`. If this is non-empty, it overrides the per-response map.
- `response_transform_map`: override transforms per response using comma-separated assignments such as `input_count_hour=log1p,key_child_count_hour=log1p`. Leave this empty when you want one global setting.
- `anova_type`: choose `2` or `3` for the `car::Anova()` tables reported below.

Examples of direct edits in the YAML block:

```yaml
params:
  model_robustness_mode: "auto"
  family1_count_age_specification: "quadratic"
  family1_duration_age_specification: "linear"
  family2_count_age_specification: "quadratic"
  family2_duration_age_specification: "linear"
  anova_type: 2
  response_transform_global: "none"
  response_transform_map: ""
  family1_participant_intercept: "without"
  family1_location_intercept: "without"
  family1_drop_fixed_terms: ["SES_num", "child_sex"]
  family1_random_slope_terms: []
  family2_participant_intercept: "with"
  family2_location_intercept: "with"
  family2_drop_fixed_terms: []
  family2_extra_fixed_terms: []
  family2_random_slope_terms: ["speaker|participant_id"]
```

Interpretation of the most common terms:

- Family 1 fixed terms usually include `speaker`, the active age terms (`age_z` or `age_z + age_z2`), the corresponding speaker-by-age interactions, `SES_num`, and `child_sex`.
- Family 2 count usually starts from `input_count_hour`, `speaker`, `input_count_hour:speaker`, the active age terms, `SES_num`, and `child_sex`.
- Family 2 duration usually starts from `input_duration_min_hour`, `speaker`, `input_duration_min_hour:speaker`, the active age terms, `SES_num`, and `child_sex`.

After you edit the parameter block, rerender the report. If `refit_models: yes`, the saved model bundles, prediction files, diagnostics, and summary tables will be regenerated using the new specification.

# 2. Load and inspect datasets

```{r load-data}
datasets_bundle <- load_analysis_datasets(write_summary = TRUE)
apply_dataset_runtime_state(datasets_bundle)

final_master <- datasets_bundle$datasets$final_master
input_data <- datasets_bundle$datasets$input_long
input_output_data <- datasets_bundle$datasets$input_output_long

show_table(
  datasets_bundle$dataset_summary,
  digits = 0,
  caption = "Analysis datasets"
)
```

## Age standardisation used by the models

```{r age-standardisation}
age_standardisation <- data.frame(
  quantity = c("Mean age in days", "SD of age in days"),
  value = c(datasets_bundle$age_days_mean, datasets_bundle$age_days_sd)
)
show_table(age_standardisation, digits = 3)
```

```{r active-model-config}
model_config_summary <- data.frame(
  setting = c(
    "family1_count age specification",
    "family1_duration age specification",
    "family2_count age specification",
    "family2_duration age specification",
    "ANOVA type",
    "Speaker contrasts"
  ),
  value = c(
    get_age_specification_name("input_count_hour", "family_1"),
    get_age_specification_name("input_duration_min_hour", "family_1"),
    get_age_specification_name("key_child_count_hour", "family_2_count"),
    get_age_specification_name("key_child_duration_min_hour", "family_2_duration"),
    analysis_options$model_config$anova_type,
    current_contrast_label()
  ),
  stringsAsFactors = FALSE
)

response_transform_summary <- data.frame(
  response = c(
    "input_count_hour",
    "input_duration_min_hour",
    "key_child_count_hour",
    "key_child_duration_min_hour"
  ),
  response_transform = vapply(
    c("input_count_hour", "input_duration_min_hour", "key_child_count_hour", "key_child_duration_min_hour"),
    get_response_transform_name,
    character(1)
  ),
  stringsAsFactors = FALSE
)

show_table(model_config_summary, digits = 0, caption = "Active modelling configuration")
show_table(response_transform_summary, digits = 0, caption = "Effective response transforms")
```

## Preprocessing audit tables

```{r preprocessing-audits}
recording_duration_audit <- read_optional_csv(file.path(analysis_paths$repo_root, "results", "recording_duration_audit.csv"))
age_validation <- read_optional_csv(file.path(analysis_paths$repo_root, "results", "age_validation.csv"))

show_table(
  if (!is.null(recording_duration_audit)) utils::head(recording_duration_audit, 12) else NULL,
  digits = 3,
  caption = "Preview of the first-day recording duration audit"
)

show_table(
  age_validation,
  digits = 3,
  caption = "Age validation checks written by the Python preprocessing pipeline"
)
```


## Speaker and participant overview

```{r sample-overview}
sample_overview <- data.frame(
  dataset = c("final_master", "input_long", "input_output_long"),
  participants = c(
    length(unique(final_master$participant_id)),
    length(unique(input_data$participant_id)),
    length(unique(input_output_data$participant_id))
  ),
  locations = c(
    length(unique(final_master$Location)),
    length(unique(input_data$Location)),
    length(unique(input_output_data$Location))
  ),
  rows = c(nrow(final_master), nrow(input_data), nrow(input_output_data))
)
show_table(sample_overview, digits = 0)

speaker_counts <- as.data.frame(table(input_data$speaker, useNA = "ifany"))
names(speaker_counts) <- c("speaker", "n_rows")
show_table(speaker_counts, digits = 0, caption = "Rows by input-speaker category")
```

# 3. Fit or load all models

# Load setup

```{r load-setup}
apply_report_environment_overrides()
source(file.path("R", "00_setup.R"))
load_required_packages(attach = FALSE)
ensure_analysis_directories()

apply_report_analysis_overrides()
apply_dataset_runtime_state(datasets_bundle)
```

# Run model scripts

```{r run-model-scripts, eval=params$refit_models}
source(file.path("R", "01_input_models.R"))
source(file.path("R", "02_input_output_models.R"))
source(file.path("R", "03_model_tables_and_plots.R"))
```


```{r fit-or-load-models}
apply_report_environment_overrides()
apply_report_analysis_overrides()
apply_dataset_runtime_state(datasets_bundle)

model_paths <- c(
  input_count_hour = file.path(analysis_paths$results_models, "input_count_hour.rds"),
  input_duration_min_hour = file.path(analysis_paths$results_models, "input_duration_min_hour.rds"),
  key_child_count_hour = file.path(analysis_paths$results_models, "key_child_count_hour.rds"),
  key_child_duration_min_hour = file.path(analysis_paths$results_models, "key_child_duration_min_hour.rds")
)

if (isTRUE(params$refit_models)) {
  input_model_bundles <- list(
    input_count_hour = fit_preregistered_model(
      input_data, "input_count_hour", "family_1", allow_gamma = TRUE
    ),
    input_duration_min_hour = fit_preregistered_model(
      input_data, "input_duration_min_hour", "family_1", allow_gamma = TRUE
    )
  )

  input_output_model_bundles <- list(
    key_child_count_hour = fit_preregistered_model(
      input_output_data, "key_child_count_hour", "family_2_count", allow_gamma = TRUE
    ),
    key_child_duration_min_hour = fit_preregistered_model(
      input_output_data, "key_child_duration_min_hour", "family_2_duration", allow_gamma = TRUE
    )
  )

  model_bundles <- c(input_model_bundles, input_output_model_bundles)

  invisible(Map(
    function(bundle, path) save_model_bundle(bundle, path),
    model_bundles,
    model_paths
  ))
} else {
  missing_models <- model_paths[!file.exists(model_paths)]
  if (length(missing_models) > 0) {
    stop(
      paste0(
        "The following saved models are missing. Render with params$refit_models = true: ",
        paste(basename(missing_models), collapse = ", ")
      )
    )
  }
  model_bundles <- lapply(model_paths, load_model_bundle)
}

selection_table <- selection_table_from_bundles(model_bundles)
utils::write.csv(
  selection_table,
  file.path(analysis_paths$results_tables, "all_model_selection.csv"),
  row.names = FALSE
)

show_table(selection_table, digits = 3, caption = "Model-selection decisions")
```

# 4. Model Family 1: Vocal input by age and speaker

## 4.1 Input count per hour

### Response inspection and selected model

```{r input-count-selection}
input_count_bundle <- model_bundles$input_count_hour
show_table(input_count_bundle$selection, digits = 3)
show_table(model_fit_table(input_count_bundle), digits = 3)
```

### Model summary

```{r input-count-summary, results='asis'}
print_model_summary(input_count_bundle)
```

### ANOVA table

```{r input-count-anova}
input_count_anova <- anova_display_table(input_count_bundle)
write_report_table(input_count_anova, "input_count_hour_anova.csv")
show_table(
  input_count_anova,
  digits = 4,
  caption = sprintf("Type-%s ANOVA for input count per hour.", analysis_options$model_config$anova_type)
)
```

### Collinearity diagnostics

```{r input-count-vif}
input_count_vif <- vif_display_table(input_count_bundle)
write_report_table(input_count_vif, "input_count_hour_vif.csv")
show_table(
  input_count_vif,
  digits = 3,
  caption = "VIF/GVIF diagnostics for input count per hour."
)
```

### Fixed effects

```{r input-count-fixed}
input_count_fixed <- fixed_effects_table(input_count_bundle)
show_table(input_count_fixed, digits = 4, caption = "Fixed effects: input count per hour")
```

### Random effects

```{r input-count-random}
show_table(random_effects_table(input_count_bundle), digits = 4)
```

### Fixed-effects forest plot

```{r input-count-forest, results='asis'}
input_count_forest <- plot_fixed_effects_forest(input_count_bundle, "input_count_hour")
show_saved_image(input_count_forest$path)
```

### Predicted input count across age and speaker

```{r input-count-prediction, results='asis', cache=TRUE}
input_count_prediction <- plot_age_speaker_predictions(
  input_count_bundle,
  input_data,
  output_stub = "input_count_by_age_speaker",
  y_label = "Predicted input count per hour",
  nsim = params$nsim
)
show_saved_image(input_count_prediction$plot_path)
```

### Prediction table preview

```{r input-count-prediction-table}
show_table(utils::head(input_count_prediction$data, 12), digits = 3)
```

### Diagnostics

```{r input-count-diagnostics, results='asis'}
input_count_diagnostics <- run_model_diagnostics(input_count_bundle)
show_table(input_count_diagnostics$summary, digits = 4)

cat("\n#### Residuals versus fitted values\n\n")
show_saved_image(input_count_diagnostics$paths$residual_plot)

cat("\n#### Residual Q-Q plot\n\n")
show_saved_image(input_count_diagnostics$paths$qq_plot)

if (!is.na(input_count_diagnostics$paths$dharma_plot)) {
  cat("\n#### DHARMa simulated residual diagnostics\n\n")
  show_saved_image(input_count_diagnostics$paths$dharma_plot)
}
```

## 4.2 Input duration in minutes per hour

### Response inspection and selected model

```{r input-duration-selection}
input_duration_bundle <- model_bundles$input_duration_min_hour
show_table(input_duration_bundle$selection, digits = 3)
show_table(model_fit_table(input_duration_bundle), digits = 3)
```

### Model summary

```{r input-duration-summary, results='asis'}
print_model_summary(input_duration_bundle)
```

### ANOVA table

```{r input-duration-anova}
input_duration_anova <- anova_display_table(input_duration_bundle)
write_report_table(input_duration_anova, "input_duration_min_hour_anova.csv")
show_table(
  input_duration_anova,
  digits = 4,
  caption = sprintf("Type-%s ANOVA for input duration in minutes per hour.", analysis_options$model_config$anova_type)
)
```

### Collinearity diagnostics

```{r input-duration-vif}
input_duration_vif <- vif_display_table(input_duration_bundle)
write_report_table(input_duration_vif, "input_duration_min_hour_vif.csv")
show_table(
  input_duration_vif,
  digits = 3,
  caption = "VIF/GVIF diagnostics for input duration in minutes per hour."
)
```

### Fixed effects

```{r input-duration-fixed}
input_duration_fixed <- fixed_effects_table(input_duration_bundle)
show_table(input_duration_fixed, digits = 4, caption = "Fixed effects: input duration")
```

### Random effects

```{r input-duration-random}
show_table(random_effects_table(input_duration_bundle), digits = 4)
```

### Fixed-effects forest plot

```{r input-duration-forest, results='asis'}
input_duration_forest <- plot_fixed_effects_forest(input_duration_bundle, "input_duration_min_hour")
show_saved_image(input_duration_forest$path)
```

### Predicted input duration across age and speaker

```{r input-duration-prediction, results='asis', cache=TRUE}
input_duration_prediction <- plot_age_speaker_predictions(
  input_duration_bundle,
  input_data,
  output_stub = "input_duration_by_age_speaker",
  y_label = "Predicted input duration (min/hour)",
  nsim = params$nsim
)
show_saved_image(input_duration_prediction$plot_path)
```

### Prediction table preview

```{r input-duration-prediction-table}
show_table(utils::head(input_duration_prediction$data, 12), digits = 3)
```

### Diagnostics

```{r input-duration-diagnostics, results='asis'}
input_duration_diagnostics <- run_model_diagnostics(input_duration_bundle)
show_table(input_duration_diagnostics$summary, digits = 4)

cat("\n#### Residuals versus fitted values\n\n")
show_saved_image(input_duration_diagnostics$paths$residual_plot)

cat("\n#### Residual Q-Q plot\n\n")
show_saved_image(input_duration_diagnostics$paths$qq_plot)

if (!is.na(input_duration_diagnostics$paths$dharma_plot)) {
  cat("\n#### DHARMa simulated residual diagnostics\n\n")
  show_saved_image(input_duration_diagnostics$paths$dharma_plot)
}
```

# 5. Model Family 2: Child output predicted by vocal input

The Family 2 formulas always include a location random intercept. The participant random intercept is controlled by `params$family2_participant_intercept`: `"with"` forces `(1|participant_id)`, `"without"` removes it, and `"auto"` tries the participant-intercept version first and falls back only if that fit fails with a hard optimisation error.

## 5.1 Key-child count per hour predicted by input count

### Response inspection and selected model

```{r child-count-selection}
child_count_bundle <- model_bundles$key_child_count_hour
show_table(child_count_bundle$selection, digits = 3)
show_table(model_fit_table(child_count_bundle), digits = 3)
```

### Model summary

```{r child-count-summary, results='asis'}
print_model_summary(child_count_bundle)
```

### ANOVA table

```{r child-count-anova}
child_count_anova <- anova_display_table(child_count_bundle)
write_report_table(child_count_anova, "key_child_count_hour_anova.csv")
show_table(
  child_count_anova,
  digits = 4,
  caption = sprintf("Type-%s ANOVA for key-child count per hour.", analysis_options$model_config$anova_type)
)
```

### Collinearity diagnostics

```{r child-count-vif}
child_count_vif <- vif_display_table(child_count_bundle)
write_report_table(child_count_vif, "key_child_count_hour_vif.csv")
show_table(
  child_count_vif,
  digits = 3,
  caption = "VIF/GVIF diagnostics for key-child count per hour."
)
```

### Fixed effects

```{r child-count-fixed}
child_count_fixed <- fixed_effects_table(child_count_bundle)
show_table(child_count_fixed, digits = 4, caption = "Fixed effects: key-child count")
```

### Random effects

```{r child-count-random}
show_table(random_effects_table(child_count_bundle), digits = 4)
```

### Fixed-effects forest plot

```{r child-count-forest, results='asis'}
child_count_forest <- plot_fixed_effects_forest(child_count_bundle, "key_child_count_hour")
show_saved_image(child_count_forest$path)
```

### Predicted child count across input count and speaker

```{r child-count-prediction, results='asis', cache=TRUE}
child_count_prediction <- plot_input_output_predictions(
  child_count_bundle,
  input_output_data,
  predictor_name = "input_count_hour",
  x_label = "Input count per hour",
  y_label = "Predicted key-child count per hour",
  output_stub = "key_child_count_by_input",
  nsim = params$nsim
)
show_saved_image(child_count_prediction$plot_path)
```

### Prediction table preview

```{r child-count-prediction-table}
show_table(utils::head(child_count_prediction$data, 12), digits = 3)
```

### Diagnostics

```{r child-count-diagnostics, results='asis'}
child_count_diagnostics <- run_model_diagnostics(child_count_bundle)
show_table(child_count_diagnostics$summary, digits = 4)

cat("\n#### Residuals versus fitted values\n\n")
show_saved_image(child_count_diagnostics$paths$residual_plot)

cat("\n#### Residual Q-Q plot\n\n")
show_saved_image(child_count_diagnostics$paths$qq_plot)

if (!is.na(child_count_diagnostics$paths$dharma_plot)) {
  cat("\n#### DHARMa simulated residual diagnostics\n\n")
  show_saved_image(child_count_diagnostics$paths$dharma_plot)
}
```

## 5.2 Key-child duration predicted by input duration

### Response inspection and selected model

```{r child-duration-selection}
child_duration_bundle <- model_bundles$key_child_duration_min_hour
show_table(child_duration_bundle$selection, digits = 3)
show_table(model_fit_table(child_duration_bundle), digits = 3)
```

### Model summary

```{r child-duration-summary, results='asis'}
print_model_summary(child_duration_bundle)
```

### ANOVA table

```{r child-duration-anova}
child_duration_anova <- anova_display_table(child_duration_bundle)
write_report_table(child_duration_anova, "key_child_duration_min_hour_anova.csv")
show_table(
  child_duration_anova,
  digits = 4,
  caption = sprintf("Type-%s ANOVA for key-child duration in minutes per hour.", analysis_options$model_config$anova_type)
)
```

### Collinearity diagnostics

```{r child-duration-vif}
child_duration_vif <- vif_display_table(child_duration_bundle)
write_report_table(child_duration_vif, "key_child_duration_min_hour_vif.csv")
show_table(
  child_duration_vif,
  digits = 3,
  caption = "VIF/GVIF diagnostics for key-child duration in minutes per hour."
)
```

### Fixed effects

```{r child-duration-fixed}
child_duration_fixed <- fixed_effects_table(child_duration_bundle)
show_table(child_duration_fixed, digits = 4, caption = "Fixed effects: key-child duration")
```

### Random effects

```{r child-duration-random}
show_table(random_effects_table(child_duration_bundle), digits = 4)
```

### Fixed-effects forest plot

```{r child-duration-forest, results='asis'}
child_duration_forest <- plot_fixed_effects_forest(child_duration_bundle, "key_child_duration_min_hour")
show_saved_image(child_duration_forest$path)
```

### Predicted child duration across input duration and speaker

```{r child-duration-prediction, results='asis', cache=TRUE}
child_duration_prediction <- plot_input_output_predictions(
  child_duration_bundle,
  input_output_data,
  predictor_name = "input_duration_min_hour",
  x_label = "Input duration (min/hour)",
  y_label = "Predicted key-child duration (min/hour)",
  output_stub = "key_child_duration_by_input",
  nsim = params$nsim
)
show_saved_image(child_duration_prediction$plot_path)
```

### Prediction table preview

```{r child-duration-prediction-table}
show_table(utils::head(child_duration_prediction$data, 12), digits = 3)
```

### Diagnostics

```{r child-duration-diagnostics, results='asis'}
child_duration_diagnostics <- run_model_diagnostics(child_duration_bundle)
show_table(child_duration_diagnostics$summary, digits = 4)

cat("\n#### Residuals versus fitted values\n\n")
show_saved_image(child_duration_diagnostics$paths$residual_plot)

cat("\n#### Residual Q-Q plot\n\n")
show_saved_image(child_duration_diagnostics$paths$qq_plot)

if (!is.na(child_duration_diagnostics$paths$dharma_plot)) {
  cat("\n#### DHARMa simulated residual diagnostics\n\n")
  show_saved_image(child_duration_diagnostics$paths$dharma_plot)
}
```

# 6. Combined result tables

## Model fit statistics

```{r combined-fit-statistics}
combined_fit <- bind_rows_safe(lapply(model_bundles, model_fit_table))
rownames(combined_fit) <- NULL
utils::write.csv(
  combined_fit,
  file.path(analysis_paths$results_tables, "combined_model_fit_statistics.csv"),
  row.names = FALSE
)
show_table(combined_fit, digits = 3)
```

## Fixed effects from all models

```{r combined-fixed-effects}
combined_fixed_effects <- bind_rows_safe(lapply(names(model_bundles), function(model_name) {
  table <- fixed_effects_table(model_bundles[[model_name]])
  table$response <- model_name
  table
}))
rownames(combined_fixed_effects) <- NULL
combined_fixed_effects <- combined_fixed_effects[, c("response", setdiff(names(combined_fixed_effects), "response"))]

utils::write.csv(
  combined_fixed_effects,
  file.path(analysis_paths$results_tables, "combined_fixed_effects.csv"),
  row.names = FALSE
)
show_table(combined_fixed_effects, digits = 4)
```

## Diagnostics summary

```{r combined-diagnostics}
diagnostics <- list(
  input_count_hour = input_count_diagnostics,
  input_duration_min_hour = input_duration_diagnostics,
  key_child_count_hour = child_count_diagnostics,
  key_child_duration_min_hour = child_duration_diagnostics
)

combined_diagnostics <- bind_rows_safe(lapply(diagnostics, function(x) x$summary))
rownames(combined_diagnostics) <- NULL
utils::write.csv(
  combined_diagnostics,
  file.path(analysis_paths$results_tables, "combined_diagnostics_summary.csv"),
  row.names = FALSE
)
show_table(combined_diagnostics, digits = 4)
```

# 7. Files generated by this report

```{r generated-files}
generated_files <- data.frame(
  output_type = c(
    "Saved model bundles",
    "Tables",
    "Prediction data",
    "Prediction and forest plots",
    "Diagnostic plots and summaries"
  ),
  directory = c(
    analysis_paths$results_models,
    analysis_paths$results_tables,
    analysis_paths$results_predictions,
    analysis_paths$results_plots,
    analysis_paths$results_diagnostics
  ),
  stringsAsFactors = FALSE
)
show_table(generated_files)
```

# 8. Reproducibility information

```{r session-info}
sessionInfo()
```
